Commit Rater

### 2015-09-22 presentations/paper/introduction.tex
Add examples of good and bad commit messages

>>>>

For example, commit messages like ``fixed a bug'' or even just ``bugfix'' serve no practical purpose, since they convey no useful information. Additionally, messages like ``The fnuction x is noww an class y'' and ``makes function x write the output to stdout and changes the format of the output of function x.'' are unpleasant to read in the Git log, because of the changing format, the typos or their verbosity. On the other hand, a message like ``Write output to stdout'' is succinct and tells the reader what it does. Coupled with similarly formatted commit messages, using tools like the Git log is a lot more pleasant.
